Two Decades of Smalltalk VM Development

### 2018-08-16 paper.tex
fixed figure with eliot
rm fig 1 and added subtitle

%% Title information
\title[Two Decades of Smalltalk VM Development]{Two Decades of Smalltalk VM Development}

@@

Figure \ref{fig:VMCompilation} depicts the main components of \openSmalltalkVM and its compilation process.
%the VM code base is written both in Slang and in C. 
The Core VM code consists of the interpreter, the JIT and the memory manager, and is written in Slang. The platform code, \emph{i.e.,} Operating System dependent code (such as file management or I/O), is written directly in C with a corresponding Smalltalk version for simulation. 
%EXPLAIN scientifically in this part - no history. + FIGURE, basic with design.

\begin{figure}[bth!]
		\centering
		\includegraphics[width=0.55\linewidth]{figures/VMCompilation}
		\caption{Cog \egb{u mean openSmalltalkVM?} VM compilation}
		\label{fig:VMCompilation}
\end{figure}

@@

\begin{figure*}[ht!]
		\centering
		\includegraphics[width=0.95\linewidth]{figures/SimulatedMemory}
		\caption{Runtime Memory and Simulated Counter-Part}
		\label{fig:SimulatedMemory}
\end{figure*}

>>>>

%% Title information
\title[Two Decades of Smalltalk VM Development]{Two Decades of Smalltalk VM Development}
\subtitle{Live VM development through Simulation Tools}

@@

The main components of \openSmalltalkVM, the interpreter, the JIT and the memory manager, are written in Slang. The platform code, \emph{i.e.,} Operating System dependent code (such as file management or I/O), is written directly in C with a corresponding Smalltalk version for simulation.

@@

\begin{figure*}[ht!]
		\centering
		\includegraphics[width=0.9\linewidth]{figures/SimulatedMemory}
		\caption{Runtime Memory and Simulated Counter-Part}
		\label{fig:SimulatedMemory}
\end{figure*}
